Detecting Hate Speech with GPT-3

### 2022-03-16 outputs/documents/paper.Rmd
Update to arxiv resubmission

The results of the mixed-category few-shot experiments are presented in Table \@ref(tab:fewshotmixed-summary), and Appendix \@ref(appendxbmuxedubsnorinstruction) provides additional detail. Among the ten sets of examples, Example Set 1 yields the best performance in terms of accuracy (91 per cent) and F1 score (87 per cent) for racist comments and Example Set 10 yields the best performance by the same metrics for sexist comments (accuracy of 89 per cent, F1 score of 85 per cent). The example set that yields the worst results in identifying racist text in terms of F1 score is Example Set 8, which has an F1 score of 70 per cent (and the lowest accuracy at 73 per cent) for this dataset. The example set that yields the worst results in identifying sexist text in terms of F1 score is Example Set 9, which has an F1 score of 69 per cent (and the lowest accuracy at 74 per cent) for this dataset. The differences between Example Sets 1, 8, 9, and 10 suggest that, although the models are provided with the same number of examples, the content of the examples also affects how the model makes inferences. Overall, the mixed-category few-shot setting performs roughly the same in terms of identifying sexist text and racist text. It is also has higher accuracy and F1 score than the zero-shot, one-shot, and single-category few-shot settings for both racist and sexist text.

@@

The unique generated answers are listed in Table \@ref(tab:fewshotmixedanswersnoinstruct). These are the response of GPT-3 that we obtain when we ask the model to classify statements, but do not provide examples that would serve to limit the responses. Under the mixed-category setting, the model is generates many answers that are out of scope. For instance, other than 'sexist', 'racist', and 'neither', we also see answers such as 'transphobic', 'hypocritical', 'Islamophobic', and 'ableist'. In some cases, the model even classifies a text passage into more than one category, such as 'sexist, racist' and 'sexist, misogynistic'. The full list contains eighty different answers instead of three.

@@

It is likely that the model is not ideal for use in hate speech detection in the zero-shot learning, one-shot learning, or single-category few-shot learning settings, as the accuracy rates are between 60 per cent and 70 per cent. @davidson2017automated, using a different model and approach, similarly find 'that almost 40 per cent of hate speech is misclassified'. And when @schick2021selfdiagnosis use GPT-2 they find a similar ability to recognize sexually explicit content, however using an alternative model - Google's T5 [@raffel2020exploring] - they find better results.

In the mixed-category few-shot setting, different example sets yield different accuracy rates for racist and sexist comments, with noticeable improvement over the single-category approaches. Mixed-category few-shot learning without instruction had noticeably better F1 scores for both racist and sexist comments than either zero-shot or one-shot learning. With instruction added, mixed-category few-shot learning performed similarly well for racist text identification, however the model performed relatively poorly in identifying sexist speech, with an F1 score of 63 per cent overall and a recall of 50 per cent meaning nearly half of the sexist comments were wrongly classified. Overall, it appears as though GPT-3 is most effective at identifying both racist and sexist comments in the mixed-category few-shot learning setting, without instruction.

@@

In order to test the impact of misspellings on hate speech classification, we examined a subset of the ETHOS dataset containing the profane words or sub-strings indicated in Table \@ref(tab:profanity) in Appendix \@ref(appendxc). These words were selected due to their prevalence in the dataset and in some cases their specific racist or sexist connotation. The comments were then edited to include misspellings or censorship (including numbers, asterisks, or dashes to remove certain vowels) on a given word or sub-string and run through the zero-shot learning process. Details of the misspellings added are also included in Table \@ref(tab:profanity). Of the 34 sexist comments and 27 racist comments considered, the misspellings and censorship impacted the classification of seven comments, all of which belonged to the racist category (results in Table \@ref(tab:misspell-results) in Appendix \@ref(appendxc)). Interestingly, three comments with added misspellings were classified as 'racist' where they had previously been classified as 'not racist'. This speaks to potential inconsistencies in the behavior of GPT-3 in understanding profanity and censorship and presents another area for further investigation.

In conclusion, with proper settings such as the inclusion of instruction and curated examples, large natural language models such as GPT-3 can identify sexist and racist text at a similar level of specificity to other methods. However, it is possible that if a user intentionally misspells profane words, the models may be less likely to identify such content as problematic. This possibility deserves further investigation due to the tendency for language to change quickly. Furthermore, the models might classify texts that contain identity terms as problematic, as they are often associated with harmful text when being targeted. Various settings should be further explored to tackle these obstacles. To shed light on why a text is misclassified, it might be appropriate to prompt GPT-3 to deliver an accompanying explanation for the decision, or to consider a larger dataset of sexist and racist content. The extent to which the identification and classification of hate speech can be explained is especially of interest for future work and is something that could be implemented on the easily available GPT-2 from OpenAI or T5 from Google.

>>>>

The results of the mixed-category few-shot experiments are presented in Table \@ref(tab:fewshotmixed-summary), and Appendix \@ref(appendxbmuxedubsnorinstruction) provides additional detail. Among the ten sets of examples, Example Set 1 yields the best performance in terms of accuracy (91 per cent) and F1 score (87 per cent) for racist comments and Example Set 10 yields the best performance by the same metrics for sexist comments (accuracy of 89 per cent, F1 score of 85 per cent). The example set that yields the worst results in identifying racist text in terms of F1 score is Example Set 8, which has an F1 score of 70 per cent (and the lowest accuracy at 73 per cent) for this dataset. The example set that yields the worst results in identifying sexist text in terms of F1 score is Example Set 9, which has an F1 score of 69 per cent (and the lowest accuracy at 74 per cent) for this dataset. The differences between Example Sets 1, 8, 9, and 10 suggest that, although the models are provided with the same number of examples, the content of the examples also affects how the model makes inferences. Overall, the mixed-category few-shot setting performs roughly the same in terms of identifying sexist text and racist text. It also has higher accuracy and F1 score than the zero-shot, one-shot, and single-category few-shot settings for both racist and sexist text.

@@

The unique generated answers are listed in Table \@ref(tab:fewshotmixedanswersnoinstruct). These are the response of GPT-3 that we obtain when we ask the model to classify statements, but do not provide examples that would serve to limit the responses. Under the mixed-category setting, the model generates many answers that are out of scope. For instance, other than 'sexist', 'racist', and 'neither', we also see answers such as 'transphobic', 'hypocritical', 'Islamophobic', and 'ableist'. In some cases, the model even classifies a text passage into more than one category, such as 'sexist, racist' and 'sexist, misogynistic'. The full list contains eighty different answers instead of three.

@@

It is likely that the model is not ideal for use in hate speech detection in the zero-shot learning, one-shot learning, or single-category few-shot learning settings, as the accuracy rates are between 60 per cent and 70 per cent. @davidson2017automated, using a different model and approach, similarly find 'that almost 40 per cent of hate speech is misclassified'. And when @schick2021selfdiagnosis use GPT-2 they find a similar ability to recognize sexually explicit content, however using an alternative model -- Google's T5 [@raffel2020exploring] -- they find better results.

In the mixed-category few-shot setting, different example sets yield different accuracy rates for racist and sexist comments, with noticeable improvement over the single-category approaches. Mixed-category few-shot learning without instruction had noticeably better F1 scores for both racist and sexist comments than either zero-shot or one-shot learning. With instruction added, mixed-category few-shot learning performed similarly well for racist text identification. But the model performed relatively poorly in terms of identifying sexist speech, with an F1 score of 63 per cent overall and a recall of 50 per cent meaning nearly half of the sexist comments were wrongly classified. Overall, it appears as though GPT-3 is most effective at identifying both racist and sexist comments in the mixed-category few-shot learning setting, without instruction.

@@

In order to test the impact of misspellings on hate speech classification, we examined a subset of the ETHOS dataset containing the profane words or sub-strings indicated in Appendix \@ref(appendxc). These words were selected due to their prevalence in the dataset and in some cases their specific racist or sexist connotation. The comments were then edited to include misspellings or censorship (including numbers, asterisks, or dashes to remove certain vowels) on a given word or sub-string and run through the zero-shot learning process. Details of the misspellings added are also included in Appendix \@ref(appendxc). Of the 34 sexist comments and 27 racist comments considered, the misspellings and censorship impacted the classification of seven comments, all of which belonged to the racist category. Interestingly, three comments with added misspellings were classified as 'racist' where they had previously been classified as 'not racist'. This speaks to potential inconsistencies in the behavior of GPT-3 in understanding profanity and censorship and presents another area for further investigation.

In conclusion, with proper settings such as the inclusion of instruction and curated examples, large natural language models such as GPT-3 can identify sexist and racist text at a similar level of specificity to other methods. However, it is possible that if a user intentionally misspells profane words, the models may be less likely to identify such content as problematic. This possibility deserves further investigation due to the tendency for language to change quickly. Furthermore, models might misclassify text that contains identity terms, as they are often associated with harmful statements. Various prompts and settings could be further explored to try to address these issues. Another especially exciting area for further research would be to fine-tune GPT-3 for this task. This means providing many examples initially, which removes the need for examples in the prompt. This is a paid service and would require funding. To better understand why text might be misclassified, it might be useful to prompt GPT-3 to deliver an accompanying explanation for the decision. Another might be to consider a larger dataset of sexist and racist content, as one of the weaknesses of our approach is the relatively small dataset. The extent to which the identification and classification of hate speech can be explained by the model is especially of interest for future work.

### 2022-03-16 outputs/documents/paper.tex
Update to arxiv resubmission

The results of the mixed-category few-shot experiments are presented in Table \ref{tab:fewshotmixed-summary}, and Appendix \ref{appendxbmuxedubsnorinstruction} provides additional detail. Among the ten sets of examples, Example Set 1 yields the best performance in terms of accuracy (91 per cent) and F1 score (87 per cent) for racist comments and Example Set 10 yields the best performance by the same metrics for sexist comments (accuracy of 89 per cent, F1 score of 85 per cent). The example set that yields the worst results in identifying racist text in terms of F1 score is Example Set 8, which has an F1 score of 70 per cent (and the lowest accuracy at 73 per cent) for this dataset. The example set that yields the worst results in identifying sexist text in terms of F1 score is Example Set 9, which has an F1 score of 69 per cent (and the lowest accuracy at 74 per cent) for this dataset. The differences between Example Sets 1, 8, 9, and 10 suggest that, although the models are provided with the same number of examples, the content of the examples also affects how the model makes inferences. Overall, the mixed-category few-shot setting performs roughly the same in terms of identifying sexist text and racist text. It is also has higher accuracy and F1 score than the zero-shot, one-shot, and single-category few-shot settings for both racist and sexist text.

@@

The unique generated answers are listed in Table \ref{tab:fewshotmixedanswersnoinstruct}. These are the response of GPT-3 that we obtain when we ask the model to classify statements, but do not provide examples that would serve to limit the responses. Under the mixed-category setting, the model is generates many answers that are out of scope. For instance, other than `sexist', `racist', and `neither', we also see answers such as `transphobic', `hypocritical', `Islamophobic', and `ableist'. In some cases, the model even classifies a text passage into more than one category, such as `sexist, racist' and `sexist, misogynistic'. The full list contains eighty different answers instead of three.

@@

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/comparison-1.pdf}
\caption{\label{fig:comparison}Comparing classification with and without an instruction}
\end{figure}

@@

It is likely that the model is not ideal for use in hate speech detection in the zero-shot learning, one-shot learning, or single-category few-shot learning settings, as the accuracy rates are between 60 per cent and 70 per cent. \citet{davidson2017automated}, using a different model and approach, similarly find `that almost 40 per cent of hate speech is misclassified'. And when \citet{schick2021selfdiagnosis} use GPT-2 they find a similar ability to recognize sexually explicit content, however using an alternative model - Google's T5 \citep{raffel2020exploring} - they find better results.

In the mixed-category few-shot setting, different example sets yield different accuracy rates for racist and sexist comments, with noticeable improvement over the single-category approaches. Mixed-category few-shot learning without instruction had noticeably better F1 scores for both racist and sexist comments than either zero-shot or one-shot learning. With instruction added, mixed-category few-shot learning performed similarly well for racist text identification, however the model performed relatively poorly in identifying sexist speech, with an F1 score of 63 per cent overall and a recall of 50 per cent meaning nearly half of the sexist comments were wrongly classified. Overall, it appears as though GPT-3 is most effective at identifying both racist and sexist comments in the mixed-category few-shot learning setting, without instruction.

@@

In order to test the impact of misspellings on hate speech classification, we examined a subset of the ETHOS dataset containing the profane words or sub-strings indicated in Table \ref{tab:profanity} in Appendix \ref{appendxc}. These words were selected due to their prevalence in the dataset and in some cases their specific racist or sexist connotation. The comments were then edited to include misspellings or censorship (including numbers, asterisks, or dashes to remove certain vowels) on a given word or sub-string and run through the zero-shot learning process. Details of the misspellings added are also included in Table \ref{tab:profanity}. Of the 34 sexist comments and 27 racist comments considered, the misspellings and censorship impacted the classification of seven comments, all of which belonged to the racist category (results in Table \ref{tab:misspell-results} in Appendix \ref{appendxc}). Interestingly, three comments with added misspellings were classified as `racist' where they had previously been classified as `not racist'. This speaks to potential inconsistencies in the behavior of GPT-3 in understanding profanity and censorship and presents another area for further investigation.

In conclusion, with proper settings such as the inclusion of instruction and curated examples, large natural language models such as GPT-3 can identify sexist and racist text at a similar level of specificity to other methods. However, it is possible that if a user intentionally misspells profane words, the models may be less likely to identify such content as problematic. This possibility deserves further investigation due to the tendency for language to change quickly. Furthermore, the models might classify texts that contain identity terms as problematic, as they are often associated with harmful text when being targeted. Various settings should be further explored to tackle these obstacles. To shed light on why a text is misclassified, it might be appropriate to prompt GPT-3 to deliver an accompanying explanation for the decision, or to consider a larger dataset of sexist and racist content. The extent to which the identification and classification of hate speech can be explained is especially of interest for future work and is something that could be implemented on the easily available GPT-2 from OpenAI or T5 from Google.

@@

\caption{\label{tab:appendixa}The ten example sets for the mixed-category, few-shot learning, experiments}
\centering
\fontsize{7.5}{9.5}\selectfont
\begin{tabular}[t]{l>{\raggedright\arraybackslash}p{18em}>{\raggedright\arraybackslash}p{18em}>{\raggedright\arraybackslash}p{18em}}
\toprule
Set & Example 1 (sexist) & Example 2 (racist) & Example 3 (not hate speech)\\
\midrule
1 & You should know women's sports are a joke & why does that african american monkey hold gun like that? & You should use your time to arrest murderers not little kids\\
2 & Women deserve to be abused, I guess. & Why do negroes tear down their own neighborhoods when a black thug gets killed by law enforcement? Must be because of low IQ. & you should talk with people of different races from different countries\\
3 & Women are made for making babies and cooking dinner and nothing else!!! & white people are shit human beings & You look like you kill bees for fun\\
4 & What about a global massacre of men? Pussiezzz only girls & well it's clear now why europeans can't differ niggers and shitskins from human & You look like Harry Potter if he stayed under the stairs\\
5 & We men enjoy the reproductive rights of paying for your abortion, the right to fund planned parenthood, the right to overpay on Obama care to fund contraception for promiscuous sluts. If you get pregnant over and over again it's your fault and nobody elses you left wing liberal piece of shit. Go be a whore. Keep spreading disease. Half of all black women have herpes. And we have the right to pay for it. You are outrageous. & We whites have higher IQ's than blacks, this is because IQ measures intelligence and we are the more evolved and superior race with a larger brain. & You look kinda dead inside, you parents must not haved loved you.\\
6 & The men are turtles...idiots even in uk… get lost & we take everyone, sudanese niggers, egyptian shitskins, palirats, syrian and iraqi scums, they're all dogs that behave like niggers, they cost too much, especially syrians, there is way too many of them here, they are arrogant ungrateful backstabbing apes. & You have the grace and composure of a rabid hyena\\
7 & That girl still need a good ass whooping, stupid ass bitch!! & U SUCK SHIT YOU BLACK FUCK & You deserve way more subscribers . The shit you say is fucking gold.\\
8 & stone throwing must be legal when against women & This sick, disgusting, white terrorist/fascist killed more than 50 innocent people. & You can see the country is fertile and green.  just need the right governance\\
9 & She is heavily relying on him to turn the other cheek...tough talking demon infested woman. & This is considered WHITE in Sweden. No wonder they accepted all those black and muslim immigrants. They are literally color blind. & you are a great brother to abbie, that family is changing the world!\\
10 & Really, I hope she get raped in the future. Raping women should be legal I think & The world would be better without white people because they stole from the black Egyptians in the before christ ages they was poor we wasnt whites  ruins everything for black people/White people have pig dicks and no shape no hips or no booty they have to get plastic surgery as us blacks get it from our mother whites brought skin cancer to america so learn some facts before you try to run us out america when we was here before yall racist ass smelly crackers and dont say you will beat my ass because you cant and if you wanna find out drop your adress√∞¬ü¬Ü¬ó√Ø¬∏¬è√∞¬ü¬í¬Ø√∞¬ü¬ô¬Ç & You are a brave man.........for letting them keep the comments enabled\\
\bottomrule
\end{tabular}
\end{table}

>>>>

The results of the mixed-category few-shot experiments are presented in Table \ref{tab:fewshotmixed-summary}, and Appendix \ref{appendxbmuxedubsnorinstruction} provides additional detail. Among the ten sets of examples, Example Set 1 yields the best performance in terms of accuracy (91 per cent) and F1 score (87 per cent) for racist comments and Example Set 10 yields the best performance by the same metrics for sexist comments (accuracy of 89 per cent, F1 score of 85 per cent). The example set that yields the worst results in identifying racist text in terms of F1 score is Example Set 8, which has an F1 score of 70 per cent (and the lowest accuracy at 73 per cent) for this dataset. The example set that yields the worst results in identifying sexist text in terms of F1 score is Example Set 9, which has an F1 score of 69 per cent (and the lowest accuracy at 74 per cent) for this dataset. The differences between Example Sets 1, 8, 9, and 10 suggest that, although the models are provided with the same number of examples, the content of the examples also affects how the model makes inferences. Overall, the mixed-category few-shot setting performs roughly the same in terms of identifying sexist text and racist text. It also has higher accuracy and F1 score than the zero-shot, one-shot, and single-category few-shot settings for both racist and sexist text.

@@

The unique generated answers are listed in Table \ref{tab:fewshotmixedanswersnoinstruct}. These are the response of GPT-3 that we obtain when we ask the model to classify statements, but do not provide examples that would serve to limit the responses. Under the mixed-category setting, the model generates many answers that are out of scope. For instance, other than `sexist', `racist', and `neither', we also see answers such as `transphobic', `hypocritical', `Islamophobic', and `ableist'. In some cases, the model even classifies a text passage into more than one category, such as `sexist, racist' and `sexist, misogynistic'. The full list contains eighty different answers instead of three.

@@

\begin{figure}
\centering
\includegraphics{comparison-1.pdf}
\caption{\label{fig:comparison}Comparing classification with and without an instruction}
\end{figure}

@@

It is likely that the model is not ideal for use in hate speech detection in the zero-shot learning, one-shot learning, or single-category few-shot learning settings, as the accuracy rates are between 60 per cent and 70 per cent. \citet{davidson2017automated}, using a different model and approach, similarly find `that almost 40 per cent of hate speech is misclassified'. And when \citet{schick2021selfdiagnosis} use GPT-2 they find a similar ability to recognize sexually explicit content, however using an alternative model -- Google's T5 \citep{raffel2020exploring} -- they find better results.

In the mixed-category few-shot setting, different example sets yield different accuracy rates for racist and sexist comments, with noticeable improvement over the single-category approaches. Mixed-category few-shot learning without instruction had noticeably better F1 scores for both racist and sexist comments than either zero-shot or one-shot learning. With instruction added, mixed-category few-shot learning performed similarly well for racist text identification. But the model performed relatively poorly in terms of identifying sexist speech, with an F1 score of 63 per cent overall and a recall of 50 per cent meaning nearly half of the sexist comments were wrongly classified. Overall, it appears as though GPT-3 is most effective at identifying both racist and sexist comments in the mixed-category few-shot learning setting, without instruction.

@@

In order to test the impact of misspellings on hate speech classification, we examined a subset of the ETHOS dataset containing the profane words or sub-strings indicated in Appendix \ref{appendxc}. These words were selected due to their prevalence in the dataset and in some cases their specific racist or sexist connotation. The comments were then edited to include misspellings or censorship (including numbers, asterisks, or dashes to remove certain vowels) on a given word or sub-string and run through the zero-shot learning process. Details of the misspellings added are also included in Appendix \ref{appendxc}. Of the 34 sexist comments and 27 racist comments considered, the misspellings and censorship impacted the classification of seven comments, all of which belonged to the racist category. Interestingly, three comments with added misspellings were classified as `racist' where they had previously been classified as `not racist'. This speaks to potential inconsistencies in the behavior of GPT-3 in understanding profanity and censorship and presents another area for further investigation.

In conclusion, with proper settings such as the inclusion of instruction and curated examples, large natural language models such as GPT-3 can identify sexist and racist text at a similar level of specificity to other methods. However, it is possible that if a user intentionally misspells profane words, the models may be less likely to identify such content as problematic. This possibility deserves further investigation due to the tendency for language to change quickly. Furthermore, models might misclassify text that contains identity terms, as they are often associated with harmful statements. Various prompts and settings could be further explored to try to address these issues. Another especially exciting area for further research would be to fine-tune GPT-3 for this task. This means providing many examples initially, which removes the need for examples in the prompt. This is a paid service and would require funding. To better understand why text might be misclassified, it might be useful to prompt GPT-3 to deliver an accompanying explanation for the decision. Another might be to consider a larger dataset of sexist and racist content, as one of the weaknesses of our approach is the relatively small dataset. The extent to which the identification and classification of hate speech can be explained is especially of interest for future work.

@@

\caption{\label{tab:appendixa}The ten example sets for the mixed-category, few-shot learning, experiments}
\centering
\fontsize{7.5}{9.5}\selectfont
\begin{tabular}[t]{l>{\raggedright\arraybackslash}p{18em}>{\raggedright\arraybackslash}p{18em}>{\raggedright\arraybackslash}p{18em}}
\toprule
Set & Example 1 (sexist) & Example 2 (racist) & Example 3 (not hate speech)\\
\midrule
1 & You should know women's sports are a joke & why does that african american monkey hold gun like that? & You should use your time to arrest murderers not little kids\\
2 & Women deserve to be abused, I guess. & Why do negroes tear down their own neighborhoods when a black thug gets killed by law enforcement? Must be because of low IQ. & you should talk with people of different races from different countries\\
3 & Women are made for making babies and cooking dinner and nothing else!!! & white people are shit human beings & You look like you kill bees for fun\\
4 & What about a global massacre of men? Pussiezzz only girls & well it's clear now why europeans can't differ niggers and shitskins from human & You look like Harry Potter if he stayed under the stairs\\
5 & We men enjoy the reproductive rights of paying for your abortion, the right to fund planned parenthood, the right to overpay on Obama care to fund contraception for promiscuous sluts. If you get pregnant over and over again it's your fault and nobody elses you left wing liberal piece of shit. Go be a whore. Keep spreading disease. Half of all black women have herpes. And we have the right to pay for it. You are outrageous. & We whites have higher IQ's than blacks, this is because IQ measures intelligence and we are the more evolved and superior race with a larger brain. & You look kinda dead inside, you parents must not haved loved you.\\
6 & The men are turtles...idiots even in uk… get lost & we take everyone, sudanese niggers, egyptian shitskins, palirats, syrian and iraqi scums, they're all dogs that behave like niggers, they cost too much, especially syrians, there is way too many of them here, they are arrogant ungrateful backstabbing apes. & You have the grace and composure of a rabid hyena\\
7 & That girl still need a good ass whooping, stupid ass bitch!! & U SUCK SHIT YOU BLACK FUCK & You deserve way more subscribers . The shit you say is fucking gold.\\
8 & stone throwing must be legal when against women & This sick, disgusting, white terrorist/fascist killed more than 50 innocent people. & You can see the country is fertile and green. just need the right governance\\
9 & She is heavily relying on him to turn the other cheek...tough talking demon infested woman. & This is considered WHITE in Sweden. No wonder they accepted all those black and muslim immigrants. They are literally color blind. & you are a great brother to abbie, that family is changing the world!\\
10 & Really, I hope she get raped in the future. Raping women should be legal I think & The world would be better without white people because they stole from the black Egyptians in the before christ ages they was poor we wasnt whites  ruins everything for black people/White people have pig dicks and no shape no hips or no booty they have to get plastic surgery as us blacks get it from our mother whites brought skin cancer to america so learn some facts before you try to run us out america when we was here before yall racist ass smelly crackers and dont say you will beat my ass because you cant and if you wanna find out drop your adress & You are a brave man.........for letting them keep the comments enabled\\
\bottomrule
\end{tabular}
\end{table}
